COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-12-12 main.tex
Rework discussion of figures 1 and 2

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that will undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

@@

Discuss figures 1 through 4 here.

A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown 
in figure \ref{fig:rtheta}. Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames. In the EJ simulation, a 
gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals 
in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped. Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect  unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}. It is worth noting, however that the spatial distribution of planetesimals shown in  figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.

The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity 
distribution of the planetesimals. This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left 
and EJ on the right. The solid vertical lines indicate the nominal locations of the mean motion resonances. Away from the resonance 
locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually 
transferred to random motions of planetesimals. The slight inward curving of the eccentricity peaks near the resonances is a 
consequence of the conservation of the Jacobi energy. As the semimajor axis of a planetesimal in MMR librates, the corresponding 
change in eccentricity is given by equation \ref{eq:tiss}.

>>>>

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

@@

We begin by examining the spatial distribution of planetesimals in both simulations. The polar position of the planetesimals at the 
end of the CJ and EJ simulations are shown in the left and right hand panels of  figure \ref{fig:rtheta}, respectively. Gaps produced by 
the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both cases. In the EJ case, a gap in the vicinity of the 5:2 MMR is also visible. 
The non-axisymmetric shape of the gaps reflects the fact that planetesimals in the vicinity of the resonances have been excited onto 
non-circular orbits. Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to 
detect unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies 
\citep{2016ApJ...818..159T, 2018ApJ...857....3T}.

The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. The top panel 
of figure \ref{fig:ae} corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines in this plot 
represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the planetesimals 
exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, the 
eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
these two quantities is described by equation \ref{eq:tiss}.

% old stuff
%A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}. Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames. In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped. Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect  unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}. It is worth noting, however that the spatial distribution of planetesimals shown in  figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.

%The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals. This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right. The solid vertical lines indicate the nominal locations of the mean motion resonances. Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals. The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy. As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.
